Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-06-17 paper/letter.tex
2 paragraphs for the rotation model

>>>>

\section*{Additional Information}

The rotation model used was based on the one explored by
\cite{GaravitoCamargo2014}. Ly-$\alpha$ photons are propagated
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation. The sources of Ly-$\alpha$ photons are located in the
center of the sphere of HI gas. Dust is not taking into account in our
simulations since their effect doesn't affect the morphology of the
Ly-$\alpha$. The radiative transfer simulations were done using
Monte Carlo simulations with the code \cite{CLARA}.

In this model rotation increases the width of the line and the flux at
the line center. Furthermore, observers at different line of sights
(LOS) angles with respect to the rotation axis of the galaxy will observe
different morphologies of the line. LOS parallel to the rotation axis
will tend to observe a double peaked line, while an observer with a LOS
perpendicular to the rotation axis will observed a single peaked
broader line.
